Make any stupid plot you want

### 2021-02-25 draft/sections/implementation.tex
reworking of bar visual transforms a bit

    def draw(self, renderer):
        # returns K, indexed on fiber then key 
        # is passed the 
        view = self.data.view(self.axes) 
        # visual channel encoding applied fiberwise 
        visual = {p: encoder(view[f] if f in self.data.FB.F else f) 
                  for p, (f, encoder) in self.transforms.items()}
        self.assemble(**visual)
        # pass configurations off to the renderer
        super().draw(renderer)
\end{minted}

The data is fetched in section \dsection\ via a \mintinline{python}{view} method on the data because the input to the artist is a section on \dtotal. The \mintinline{python}{view} method takes the \mintinline{python}{axes} attribute because it provides the region in graphic coordinates \gbase\ that we can use to query back into data to select a subset as discussed in section~\ref{sec:data_sheaf_stalk}. The \vchannel\ functions are then applied to the data to generate the visual section \vsection\ that here is the object \mintinline{python}{visual}. We allow for fixed visual parameter, such as setting a constant color for all sections, by verifying that the named component is in \dfiber\ before accessing the data. If the data component name is not in \dfiber\, this is interpreted to mean this component is a thickening of \vtotal that could be pulled back to \dtotal\ via an inverse identity \vchannel. The conversion from data to visual space is simplified here to show that it is the encoding \vchannel\ applied to the component.

@@

\begin{minted}{python}
class Line(mcollections.LineCollection):
    def assemble(self, x, y, color='C0'):
            #assemble line marks as set of segments 
            segments = [np.vstack((vx, vy)).T for vx, vy 
                        in zip(x, y)]
            self.set_segments(segments)
            self.set_color(color)

\end{minted}
In the \mintinline{python}{Line} artist, \mintinline{python}{view} returns a table of edges. Each edge consists of (x,y) points sampled along the line defined by the edge and information such as the color of the edge. As with \mintinline{python}{Point}, the data is then converted into visual variables. In \mintinline{python}{assemble}, this visual representation is composed into a set of line segments, where each segement is the array generated by \mintinline{python}{np.vstack((vx, vy))}. Then the colors of each line segment are set. The colors are guaranteed to correspond to the correct segment because of the atomicity constraint on view.

\begin{figure}[H]
    \begin{subfigure}{0.5\textwidth}
        \includegraphics[width=\textwidth]{figures/code/bar_v.png}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \includegraphics[width=\textwidth]{figures/code/bar_h.png}
    \end{subfigure}
    \caption{Frequency of Penguin types visualized as discrete bars. }
    \label{fig:code_bar_simple}
\end{figure}
The bar charts in figure~\ref{fig:code_bar_simple} are generated with a \mintinline{python}{Bar} artist. The have the same required \vfiber\ components of (position, length), but in \mintinline{pyton}{__init__} of \mintinline{python}{Bar} an additional parameter is set, \texttt{orientation} which controls whether the bars are arranged vertically or horizontally. This paramter only applies holistically to the graphic and never to individual data parameters, and highlights how the model encourages explicit differentiation between parameters in \vtotal\ and graphic parameters applied directly to \vmarkd\.

\begin{minted}{python}
class Bar(mcollections.Collection):
    def __init__(self, data, transforms, orientation = 'v', *args, **kwargs):
        # parameter of the graphic
        self.orientation = orientation 
        super().__init__(*args, **kwargs)
        self.data = data
        self.transforms = transforms

    def assemble(self, visual):
        #set some defaults
        visual.setdefault('width', itertools.repeat(0.8))
        visual.setdefault('floor', itertools.repeat(0))
        visual.setdefault('facecolors', 'C0')
        #build bar glyphs based on graphic parameter
        if self.orientation in {'vertical', 'v'}:
            order = ['position', 'width', 'floor', 'length']
        elif self.orientation in {'horizontal', 'h'}:
            order = ['floor', 'length', 'position', 'width']

        verts = [[(x, y), (x, y+yo), (x+xo, y+yo), (x+xo, y), (x, y)] 
                for (x, xo, y, yo) in zip(*[visual[k] for k in order])]

        self._paths = [mpath.Path(xy, closed=True) for xy in verts]
        self.set_edgecolors('k')
        self.set_facecolors(visual['facecolors'])

\end{minted}
The \mintinline{python}{draw} method is the same as the one in the artist example~\ref{code:artist} so is ommitted here.  This bar underpins a rudimentary version of the complex \plus operator such that we can specify multiple components to map to the same visual components without requiring th components to be individually specified in the \mintinline{python}{transforms} dictionary. The implementation of this support is slightly more complicated than the simple case, but not in a way that is useful for understanding the framework. The \mintinline{python}{assemble} function constructs bars and sets their edge color to black. Defaults are provided for 'width' and 'floor' to make this function more reusable. Typically the defaults are used for the type of chart shown in figure~\ref{fig:code_bar_simple}, but these visual variables are often set when building composite versions of this chart type as discussed in section~\ref{sec:code_case_study}.

>>>>

    def draw(self, renderer):
        # returns K, indexed on fiber then key 
        # is passed the 
        view = self.data.view(self.axes) 
        # visual channel encoding applied fiberwise 
        visual = {p: t['encoder'](view[t['name']])
                  for p, t in self.transforms.items()}
        self.assemble(**visual)
        # pass configurations off to the renderer
        super().draw(renderer)
\end{minted}

The data is fetched in section \dsection\ via a \mintinline{python}{view} method on the data because the input to the artist is a section on \dtotal. The \mintinline{python}{view} method takes the \mintinline{python}{axes} attribute because it provides the region in graphic coordinates \gbase\ that we can use to query back into data to select a subset as discussed in section~\ref{sec:data_sheaf_stalk}. The \vchannel\ functions are then applied to the data to generate the visual section \vsection\ that here is the object \mintinline{python}{visual}. The conversion from data to visual space is simplified here to directly show that it is the encoding \vchannel\ applied to the component. In the full implementation, we allow for fixed visual parameter, such as setting a constant color for all sections, by verifying that the named component is in \dfiber\ before accessing the data. If the data component name is not in \dfiber\, this is interpreted to mean this component is a thickening of \vtotal that could be pulled back to \dtotal\ via an inverse identity \vchannel.

@@

\begin{minted}{python}
class Line(mcollections.LineCollection):
    def assemble(self, x, y, color='C0'):
            #assemble line marks as set of segments 
            segments = [np.vstack((vx, vy)).T for vx, vy 
                        in zip(x, y)]
            self.set_segments(segments)
            self.set_color(color)
\end{minted}
In the \mintinline{python}{Line} artist, \mintinline{python}{view} returns a table of edges. Each edge consists of (x,y) points sampled along the line defined by the edge and information such as the color of the edge. As with \mintinline{python}{Point}, the data is then converted into visual variables. In \mintinline{python}{assemble}, this visual representation is composed into a set of line segments, where each segement is the array generated by \mintinline{python}{np.vstack((vx, vy))}. Then the colors of each line segment are set. The colors are guaranteed to correspond to the correct segment because of the atomicity constraint on view.

\begin{figure}[H]
    \begin{subfigure}{0.5\textwidth}
        \includegraphics[width=\textwidth]{figures/code/bar_v.png}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \includegraphics[width=\textwidth]{figures/code/bar_h.png}
    \end{subfigure}
    \caption{Frequency of Penguin types visualized as discrete bars. }
    \label{fig:code_bar_simple}
\end{figure}
The bar charts in figure~\ref{fig:code_bar_simple} are generated with a \mintinline{python}{Bar} artist. The have the same required \vfiber\ components of (position, length), but in \mintinline{pyton}{__init__} of \mintinline{python}{Bar} an additional parameter is set, \texttt{orientation} which controls whether the bars are arranged vertically or horizontally. This parameter only applies holistically to the graphic and never to individual data parameters, and highlights how the model encourages explicit differentiation between parameters in \vtotal\ and graphic parameters applied directly to \vmarkd\.

\begin{minted}{python}

\end{minted}
The \mintinline{python}{draw} method here has a more complex unpacking of visual encodings to support passing in visual component data directly. This is necessary to build composite artists out ouf of this bar artists.

This bar underpins a rudimentary version of the complex \plus operator such that we can specify multiple components to map to the same visual components without requiring th components to be individually specified in the \mintinline{python}{transforms} dictionary. The implementation of this support is slightly more complicated than the simple case, but not in a way that is useful for understanding the framework. The \mintinline{python}{assemble} function constructs bars and sets their edge color to black. Defaults are provided for 'width' and 'floor' to make this function more reusable. Typically the defaults are used for the type of chart shown in figure~\ref{fig:code_bar_simple}, but these visual variables are often set when building composite versions of this chart type as discussed in section~\ref{sec:code_case_study}.
